Handling String-Number Conversion in String Constraint Solving

### 2019-11-17 draft.tex
little things

\paragraph{Concatenation of PFAs}
Concatenation is another operation over PFAs needed when constructing underapproximations. Its implementation is straightforward, connect the final state of the first PFA with the initial state of the second by an $\epsilon$-transition. Sinco our automata do not allow $\epsilon$-transition, 
the connecting transition is labeled by a fres variable $v_\epsilon$ and the constraint $v_\epsilon$ is added to the interpretation contraint.

>>>>

\paragraph{Concatenation of PFAs}
Concatenation is another operation over PFAs needed when constructing underapproximations. Its implementation is straightforward, connect the final state of the first PFA with the initial state of the second by an $\epsilon$-transition. Since our automata do not allow transition directly labeled by $\epsilon$, 
the $\epsilon$-transition is labeled by a fresh variable $v_\epsilon$ contrained by the constraint $v_\epsilon = \epsilon$.
